--- 
title: "`r emo::ji('joker')` Probability I"
subtitle: "Spring Semester 2021"
author: "Dr. Daniel Flores Agreda (based on the Lecture by Prof. Davide La Vecchia)"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "Course Materials"
code_folding: hide 
toc-title: "Probability I - Spring 2021"
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = 'center')
```

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```


```{r}
library(tidyverse)
library(emo)
```


# About this lecture {-}


```{r ,echo = FALSE, fig.align='center'}
  knitr::include_url("https://giant.gfycat.com/ApprehensiveEarnestFlounder.mp4")
```

```{r, eval= FALSE, echo = FALSE}
library(plinko)
library(dplyr)
library(ggplot2)
library(distributional)
library(ggdist)

theme_set(theme_ggdist())

# You can construct plinko boards using distributions from the distributional package:

set.seed(1234)  # for reproducibility

dist = dist_normal(2, 1)
board = plinko_board(dist, n_bin = 1000, n_ball = 1000)
autoplot(board)

board %>%
  tween_balls(frame_mult = 4) %>%
  animate(height = 350, fps = 30, end_pause = 2 * 30)
```


Hello and Welcome to this introductory Lecture in Probability! 

This "book" is a complement to the Lecture. 

## The contents in a nutshell {-}

The Lecture is divided in the following units, and each unit contains several themes. 

| Number| Name  | Themes |
|:------:|:-------|:-------|
| 1 |**Introduction** | Intro, Mathematics reminder and Combinatorics. |
| 2 |**Basic calculus for probability** | Random variables, Trees, Venn diagram, Conditional probability, Independence & Bayes' theorem. | 
| 3 | **Discrete random variables**| Definitions, Expected value and variance,  Binomial, Poisson, Negative binomial and Hypergeometric |
| 4 | **Continuous random variables** | Definitions, Expected value and variance, Cumulative distribution function (cdf) and Probability density function (pdf), Some important examples: Uniform, Exponential, Gamma, Normal, logNormal, Student's..., Relationships | 
| 5 | **Bivariate random variables** | | 
| 6 | **Limit theorems** | Weak Law of Large Numbers (WLLN) and Central Limit Theorem (CLT) |
| 7 | **Elements of Simulation** | Numerical methods for the simulation of random variable with a given CDF. | 


## Practical information {-}

### Who we are {-}

```{r}
library(htmltools)

card_component <- function(name, title, portrait, e_mail) {
  div(
    img(src = portrait,
        alt = name, 
        style = "
        border-radius: 100%;
        object-fit: cover;
        width: 200px;
        height: 200px;"), 
    div(
      h5(name),
      h6(title), 
      a(e_mail)
    )
  )
}
```


```{r}
lecturers <- tibble(
  name = c("Daniel FLORES AGREDA", "Edoardo VIGNOTTO"),
  title = c("Data Science Course Developer and Instructor" , "Teaching and Research Assistant"),
  portrait = c(
    "https://d33wubrfki0l68.cloudfront.net/bb2b2f1c0fb1d52f4c61c9bacdc49dcbfc4c756c/58288/daniel.3c796e13.jpg",
    "https://www.unige.ch/gsem/files/cache/5825d0668aa3e7ad3ff8ec085e7f3498_f3901.jpg"), 
  e_mail = c("Daniel.Flores@unige.ch", "Edoardo.Vignotto@unige.ch")
)
```

```{r}
lecturers %>%
  purrr::pmap(card_component) %>%
  div(
    style = "display: grid;
    grid-template-columns: repeat(auto-fill, minmax(220px, 1fr));
    grid-gap: 25px 30px;"
  ) %>%
  doRenderTags()
```





### Lectures {-}

The Lectures will take place over [Zoom](https://unige.zoom.us/j/7938361073) on **Thursdays** from **12h to 14h**. 

- Lectures will consist on a presentation of the contents of the class. 

- During the class, there will be some exercises. You are invited to download the app [Wooclap]()

- On certain occasions, a video of the week presentation will be available beforehand. In those cases, the session will be replaced by a quiz and Q\& A session. 

### Exercises {-}

Exercise sessions will take place on **Thursdays**  from **16 to 18** over [Zoom](https://unige.zoom.us/j/7938361073)

- Problem sets are not graded

- The problem set will be posted on-line one week before

- Solutions will be made available [Moodle](https://moodle.unige.ch/course/view.php?id=7133)


### Tools {-}

- [Moodle](https://moodle.unige.ch/course/view.php?id=7133): 

- [Wooclap]() : Web application allowing to choose among a wide range of questions (multiple choice, word cloud, visual questions...)

- [Speakup]() : Platform allowing students to ask questions anonymously. Possibility to remove anonymity with integration on Moodle.

#### Reference {-}

- **Textbook** [_A first course in probability_](https://www.pearson.com/us/higher-education/product/Ross-First-Course-in-Probability-A-9th-Edition/9780321794772.html), S. Ross (any edition), Ed: Pearson New International Edition, cited as @ross2014first
