--- 
title: "Probability I"
author: "Dr. Daniel Flores Agreda (based on the notes by Prof. Davide La Vecchia)"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "Course Materials"
code_folding: hide 
toc-title: "Probability I - Spring 2021"
---

# About this Lecture {-}

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

```{r}
library(emo)
```

<mark>
  Insert image here.
</mark>

Hello and welcome to this Lecture. 


### Course Contents {-}

This Lecture in 

1. Introduction
  
2. Basic calculus for probability
  <!-- - Random variables   -->
  <!-- - Trees -->
  <!-- - Venn diagram -->
  <!-- - Conditional probability  -->
  <!-- - Independence & Bayes' theorem -->
  <!-- - ... -->
3. Discrete random variables
  <!-- - Definitions -->
  <!-- - Expected value and variance -->
  <!-- - Binomial -->
  <!-- - Poisson -->
  <!-- - Negative binomial and hypergeometric -->
4. Continuous random variables
  <!-- - Definitions -->
  <!-- - Expected value and variance -->
  <!-- - Cumulative distribution function (cdf) and Probability density function (pdf) -->
  <!-- - Some important examples: Uniform, Exponential, Gamma, Normal, logNormal, Student's... -->
  <!-- - Relationships -->
5. Bivariate random variables
6. Limit theorems
  <!-- - Weak Law of Large Numbers (WLLN) and Central Limit Theorem (CLT) -->
7. Elements of simulations 
  <!-- - numerical methods for the simulation of random variable with a given CDF... -->

## Practical information {-}

### Hours {-}

- Lectures : Thursday. from 12 to 14 (MR280) 

- Exercises (exercise sheets \& solutions available on Moodle):  
  - Thur. from 16 to 18 (MS130) 

- **Exam:**  Written exam **open-book, 2 hrs**

- **Book:** _A first course in probability_, S. Ross (any edition), Ed: Pearson New International Edition.
