--- 
title: "`r emo::ji('joker')` Probability I"
subtitle: "Course Notes"
author: "Dr. Daniel Flores Agreda (based on the Lecture by Prof. Davide La Vecchia)"
site: bookdown::bookdown_site
output: bookdown::bs4_book
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "Course Materials"
code_folding: hide 
toc-title: "Probability I - Spring 2021"
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = 'center')
```

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```


```{r}
library(tidyverse)
library(emo)
```


# About this lecture {-}

<center> 

```{r ,echo = FALSE, , out.width = "75%"}
  knitr::include_url("https://giant.gfycat.com/ApprehensiveEarnestFlounder.mp4")
```

Hello and Welcome to this introductory Lecture in Probability! 

These Course Notes are a complement to the Lecture Probability I. 

</center> 

## Contents {-}

The Lecture is divided in the following Chapters, and each Chapter contains several themes.

| Number| Name  | Themes | Status |
|:------:|:-------|:-------|:-------:| 
| 1 |**Introduction** | Intro, Mathematics reminder and Combinatorics. | ☑️ | 
| 2 |**Elements of Set Theory For Probability** | Random variables, Trees, Venn diagram, Conditional probability, Independence & Bayes' theorem. | ☑️ | 
| 3 |**Axiomatic Foundations of Probability** | Probability Axioms, Illustrations of use | ☑️ | 
| 4 | **Discrete random variables**| Definitions, Expected value and variance,  Binomial, Poisson, Negative binomial and Hypergeometric | 🔧 | 
| 5 | **Continuous random variables** | Definitions, Expected value and variance, Cumulative distribution function (cdf) and Probability density function (pdf), Some important examples: Uniform, Exponential, Gamma, Normal, logNormal, Student's t, Relationships | 🔧 |
| 6 | **Limit Theorems** | Weak Law of Large Numbers (WLLN) and Central Limit Theorem (CLT) | 📝 | 
| 7 | **Bivariate Discrete Random Variables** | | 📝 |
| 8 | **Elements of Simulation** | Numerical methods for the simulation of random variable with a given CDF. | 📝 |

- ☑️ = Ready (almost surely with typos).
- 🔧 = Fine-tuning.
- 📝 = Writing.

## Practical information {-}

### Who we are {-}

```{r}
library(htmltools)

card_component <- function(name, title, portrait, e_mail) {
  div(
    img(src = portrait,
        alt = name, 
        style = "
        border-radius: 100%;
        object-fit: cover;
        width: 200px;
        height: 200px;"), 
    div(
      h5(name),
      h6(title), 
      a(e_mail)
    )
  )
}
```


```{r}
lecturers <- tibble(
  name = c("Daniel FLORES AGREDA", "Edoardo VIGNOTTO"),
  title = c("Data Science Course Developer and Instructor" , "Teaching and Research Assistant"),
  portrait = c(
    "https://d33wubrfki0l68.cloudfront.net/bb2b2f1c0fb1d52f4c61c9bacdc49dcbfc4c756c/58288/daniel.3c796e13.jpg",
    "https://www.unige.ch/gsem/files/cache/5825d0668aa3e7ad3ff8ec085e7f3498_f3901.jpg"), 
  e_mail = c("Daniel.Flores@unige.ch", "Edoardo.Vignotto@unige.ch")
)
```

```{r}
lecturers %>%
  purrr::pmap(card_component) %>%
  div(
    style = "display: grid;
    grid-template-columns: repeat(auto-fill, minmax(220px, 1fr));
    grid-gap: 25px 30px;"
  ) %>%
  doRenderTags()
```


### Lectures {-}

The Lectures will take place over [Zoom](https://unige.zoom.us/j/98257116213?pwd=S2VkVWwzbys5SzcyeUMyVERlV1c2UT09) on **Thursdays** from **12h to 14h**. 

- Lectures will consist on a presentation of the contents of the class. 

- During the class, there will be some exercises. You are invited to download the app [Wooclap](https://www.wooclap.com)

### Exercises {-}

- **Q&A sessions on the exercises will take place on Thursdays from 16 to 18 over Zoom**. We will soon be making available a platform to raise and vote on your questions.

- **The problem set and their solutions will be posted on-line one week before**. You must are warmly reminded to try the exercises by yourselves before looking at the solution. If you are blocked in a point, or you don't understand a step, you can raise your questions to the T.A.

- **Problem sets are not graded.**

### Tools {-}

- [Moodle](https://moodle.unige.ch/course/view.php?id=7133). All the resources of the class will be available in this page.

- [Wooclap](https://www.wooclap.com) A Web application allowing to choose among a wide range of questions (multiple choice, word cloud, visual questions)


#### Reference {-}

Aside from these Course Notes, you can check: 

- [_A first course in probability_](https://www.pearson.com/us/higher-education/product/Ross-First-Course-in-Probability-A-9th-Edition/9780321794772.html), S. Ross (any edition), Ed: Pearson New International Edition, cited as @ross2014first.  

We will not be following the content of this book beat-by-beat, but it is available for reference and/or in case you want a different explanation or go deeper in the context of the Course.
